Exploration

### 2018-03-02 exploration.Rmd
formatting

  #---- fill IPM matrices
  ## Underlying Truth: use assigned slopes
  b <- lo + c(0:n)*(hi - lo)/n  # boundary points
  y <- 0.5*(b[1:n] + b[2:(n+1)])  # mesh points
  h <- y[2] - y[1]  # step size
  z.i <- 2:(n+1)  # continuous stage matrix indices
  ### growth and survival
  G.mx <- h*outer(y, y, calc_grow, p=p, n_gz=n_gz, X.g=X_g[i,])
  S.v <- calc_surv(y, p=p, n_sz=n_sz, X.s=X_s[i,])
  ### Fix eviction of individuals below/above size limits
  for(k in 1:(n/2)) G.mx[1,k] <- G.mx[1,k] + 1 - sum(G.mx[,k])
  for(k in (n/2+1):n) G.mx[n,k] <- G.mx[n,k] + 1 - sum(G.mx[,k])
  ### fill P, F, and K
  for(k in z.i) Ps[k,z.i,i] <- G.mx[k-1,]*S.v
  Ps[1,1,i] <- calc_staySB(p)
  Fs[z.i,z.i,i] <- h*outer(y, y, calc_rcrDir, p=p, n_seedz=n_seedz,
                             n_flz=n_flz, X.seed=X_seed[i,], X.fl=X_fl[i,])
  Fs[1,z.i,i] <- calc_addSB(y, p=p, n_seedz=n_seedz, n_flz=n_flz, 
                            X.seed=X_seed[i,], X.fl=X_fl[i,])
  Fs[z.i,1,i] <- calc_rcrSB(y, p)
  IPMs[,,i] <- Ps[,,i] + Fs[,,i]

>>>>

  #---- Truth: use assigned slopes to fill IPM matrix
  b <- lo + c(0:n)*(hi - lo)/n  # boundary points
  y <- 0.5*(b[1:n] + b[2:(n+1)])  # mesh points
  h <- y[2] - y[1]  # step size
  z.i <- 2:(n+1)  # continuous stage matrix indices
  ### growth and survival
  G.mx <- h*outer(y, y, calc_grow, p=p, n_gz=n_gz, X.g=X_g[i,])
  S.v <- calc_surv(y, p=p, n_sz=n_sz, X.s=X_s[i,])
  ### Fix eviction of individuals below/above size limits
  for(k in 1:(n/2)) G.mx[1,k] <- G.mx[1,k] + 1 - sum(G.mx[,k])
  for(k in (n/2+1):n) G.mx[n,k] <- G.mx[n,k] + 1 - sum(G.mx[,k])
  ### fill P, F, and K
  for(k in z.i) Ps[k,z.i,i] <- G.mx[k-1,]*S.v
  Ps[1,1,i] <- calc_staySB(p)
  Fs[z.i,z.i,i] <- h*outer(y, y, calc_rcrDir, p=p, n_seedz=n_seedz,
                             n_flz=n_flz, X.seed=X_seed[i,], X.fl=X_fl[i,])
  Fs[1,z.i,i] <- calc_addSB(y, p=p, n_seedz=n_seedz, n_flz=n_flz, 
                            X.seed=X_seed[i,], X.fl=X_fl[i,])
  Fs[z.i,1,i] <- calc_rcrSB(y, p)
  IPMs[,,i] <- Ps[,,i] + Fs[,,i]
